### 2008-09-25 Latex/H2Preview/ResponseToReviewers/Response.txt

In earlier work on discrete-time H2/LQG preview control, the theoretical results have been developed with reference to particular applications, which has led to restrictions in the classes of problems which may be tackled by these results. To the best of the authors knowledge, there is no single reference which provides a complete set of tools for synthesising H2 preview controllers that solve realistic design problems. This is the purpose of the present work. In pursuit of this goal, we solve a very general preview problem, within which more complex preview problems may be embedded, such as the preview tracking with integral action problem illustrated in Figure 14. Contributions made by this paper include:

1. a first complete solution to the preview problem in Figure 1;
2. an efficient method for finding the H2 norm of the closed-loop system;
3. a method for evaluating the norm reduction due to preview as N -> inf;
4. a low-order output feedback controller implementation;
5. a low-order feedforward controller implementation.
Points 2 and 3 are useful in that they enable one to answer the following questions:
(a) What is the preview length required to achieve a given performance specification?
(b) What is the maximum possible reduction in the closed-loop H2-norm through preview?
(c) If a large amount of preview is available, how much should be used?

As the reviewers suggest, both and Tadmor & Mirkin (2005) and Zhang & Xie (2007) consider a  similar problem in the Hinf setting. However, these papers do not provide a treatment of the output feedback case, and their formulation does not allow the inclusion of frequency dependent weighting functions. Unlike standard H2 or Hinf problems, the extension to these cases is not straightforward, and so these papers could only be used to derive a very restricted solution to the H2 preview problem. In fact, to the best of the authors' knowledge, the only paper which tackles efficient synthesis and implementation of generic output feedback Hinf preview controllers  is Hazell & Limebeer (2008). Whilst a general H2 synthesis procedure could be obtained as a special case of this paper, it would result in an unnecessary level of algorithmic complexity, and analysis of the H2 norm reduction would not be possible.

Reviewer 1 suggests that the full information and output feedback sections may be merged. However, the vast majority of the full information section is concerned with efficient computation of the full information controller gain matrices, which must also be computed for the output feedback controller. We therefore feel that merging these sections would lead to little length reduction and could damage the clarity of the exposition.

The associate editor suggests that the Reviewers would like some experimental results included. However, we do not seem to be able to find any reference to such a request within the reviewers comments. In our view, the purpose of this paper is not to make the case for using Preview Control in practical applications - that case has already been made by many papers appearing in the literature - but instead to extend the class of problems which can be tackled, and to provide a single clear and generic framework on which to base Preview Controller designs. As such, it is our opinion that including a case study may add considerable length without necessarily adding much value. We have now included a reference and a link to the first author's thesis, which does contain several substantial case studies that employ the algorithms described in this paper.

If, on the other hand, the purpose of adding an example would be simply to convince the reader that the algorithms work, then the example already given in section 8.2 should fulfill that role.

References:
=========
A. Hazell and D. J. N. Limebeer. An efficient algorithm for discrete-time Hinfinity preview control. Automatica, 44(9):2441–2448, 2008.

G. Tadmor and L. Mirkin. Hinf control and estimation with preview-part II: fixed-size ARE solutions in discrete time. IEEE Trans Auto Control, 50(1):29–40, 2005.

H. Zhang, L. Xie, and G. Duan. Hinfinity control of discrete-time systems with multiple input delays. IEEE Trans Auto Control, 52(2):271–283, 2007.

### 2008-09-25 Latex/H2Preview/H2PrevConcs.tex
Version sent to David 25/9/08

========================

>>>>

========================
Beginnings of a re-write:

Preview control has been studied for over three decades and a number of theoretical results can be found in the technical literature. Preview control has also been employed in a variety of contempory applications in mechanical engineering. These include active automotive suspension control \cite{Roh_1999_Stoc_Opt_Prev,Marzbanrad_2004_SuspPrev}, helicopter flight control \cite{Paulino_2006_PreviewRotorcraftAffine}, 
and driver steering control \cite{Cole_2006_PredictiveAndPreviewSteeringControl}. In earlier work on discrete-time H2/LQG preview control, the theoretical results have been developed with reference to particular applications, which has led to restrictions in the classes of problems which may be tackled by these results. To the best of the authors knowledge, there is no single reference which provides a complete set of tools for synthesising $\htwo$ preview controllers that solve realistic design problems. This is the purpose of the present work. In pursuit of this goal, we solve a very general preview problem, within which more complex preview problems may be embedded, such as the preview tracking with integral action problem illustrated in Figure \ref{fig:TrackSysIntegDesign}.
In our solution, the open-loop system is controlled by a two-degree-of-freedom controller, which optimizes the system response to a combination of previewable and non-previewable exogenous inputs. Efficient algorithms have been presented for solving the two standard LQG Riccati equations, as well as computing the perfect information controller gains.

Contributions made by this paper include:
\begin{enumerate}
\item a first complete solution to the preview problem in Figure 1;
\item an efficient method for finding the $\htwo$ norm of the closed-loop system;
\item a method for evaluating the norm reduction due to preview as $N \rightarrow \infty$;
\item a low-order output-feedback controller implementation;
\item a low-order feedforward controller implementation.
\end{enumerate}

### 2008-09-25 Latex/H2Preview/H2PrevIntro.tex
Version sent to David 25/9/08

A pole-zero plot of the optimal controller is given in Figure \ref{fig:PZforSISOPrevH2} for the case where $c_z=1.05$, $G_o(\z)=(1-\z c_z)/(\z-0.5)$, and $N=20$. Notice the almost pole-zero cancellation on the real axis. In the limit $N\rightarrow \infty$ cancellation occurs. 
\begin{figure}
\begin{center}
\includegraphics[width=0.7\columnwidth]{./diags/SimpleExamplePZPlot2.eps}
\end{center}
\caption{Pole-zero plot of the $\htwo$-optimal $K(\z)$ for the case where $c_z=1.05$, $G_o(\z)=(1-\z c_z)/(z-0.5)$ and $N=20$.   }
\label{fig:PZforSISOPrevH2}
\end{figure}
This simple preview problem highlights several important features that will be carried over into the more complex problem treated in this paper. In particular:
\begin{enumerate}
\item The preview action is captured in an {FIR} block having order $N$.
\item The remainder of the controller (the {IIR} part) has order equal to the plant order.
\item The preview length (N) required to achieve 95\% (for example) of the maximum norm reduction due to preview, is affected by the position of {NMP} zeros. 
\end{enumerate}

Point 3 merits further discussion. A central tenet of this paper is that the preview length could be sufficiently large that solution of the associated {DARE} is computationally intractable. However, it might be argued that it is never necessary to use a large preview length because one could simply reduce the sampling rate until $N$ becomes sufficiently small.  In \cite{Middleteon_2004_PrevPerf}, an example similar to Figure \ref{fig:SimpleSISOPrevexample} is treated in continuous-time, and it is found that the required preview \textit{time} is purely a function of the position of the continuous-time zero. The discrete-time equivalent of this result is that: for a given performance improvement, the preview time $NT_s$ (where $T_s$ represents the sample time) is determined by the position of the \textit{continuous-time} zero. This fact can be seen by considering the effect of $T_s$ on the magnitude of $c_z$ in (\ref{eqn:H2normsimple}). Typically, the sampling rate is determined by the frequency at which tracking or disturbance rejection is required, and also by the frequency of any unstable poles \citep{Houpis_1991_DigitalControlSystems}. It therefore follows that a combination of low frequency zeros (which impose a large $NT_s$), and higher frequency performance specifications (which impose a low $T_s$), would lead unavoidably to a large preview length ($N$).% in order to achieve 95\% of the maximum available benefit due to preview.

>>>>

A pole-zero plot of the optimal controller is given in Figure \ref{fig:PZforSISOPrevH2} for the case where $c_z=1.05$, $G_o(\z)=(1-\z c_z)/(\z-0.5)$, and $N=20$. Notice the almost pole-zero cancellation on the real axis. In the limit $N\rightarrow \infty$ cancellation occurs. 
\begin{figure}
\begin{center}
\includegraphics[width=8cm]{./diags/SimpleExamplePZPlot2.eps}
\end{center}
\caption{Pole-zero plot of the $\htwo$-optimal $K(\z)$ for the case where $c_z=1.05$, $G_o(\z)=(1-\z c_z)/(z-0.5)$ and $N=20$.   }
\label{fig:PZforSISOPrevH2}
\end{figure}
This simple preview problem highlights several important features that will be carried over into the more complex problem treated in this paper. In particular:
\begin{enumerate}
\item The preview action is captured in an {FIR} block having order $N$.
\item The remainder of the controller (the {IIR} part) has order equal to the plant order.
\item The preview length (N) required to achieve 95\% (for example) of the maximum norm reduction due to preview, is affected by the position of {NMP} zeros. 
\end{enumerate}

Point 3 merits further discussion. A central tenet of this paper is that the preview length could be sufficiently large that solution of the associated {DARE} is computationally intractable. However, it might be argued that it is never necessary to use a large preview length because one could simply reduce the sampling rate until $N$ becomes sufficiently small.  In \cite{Middleteon_2004_PrevPerf}, an example similar to Figure \ref{fig:SimpleSISOPrev} is treated in continuous-time, and it is found that the required preview \textit{time} is purely a function of the position of the continuous-time zero. The discrete-time equivalent of this result is: for a given performance improvement, the preview time $NT_s$ (where $T_s$ represents the sample time) is determined by the position of the continuous-time zero. This fact can be seen by considering the effect of $T_s$ on the magnitude of $c_z$ in (\ref{eqn:H2normsimple}). Typically, the sampling rate is determined by the frequency at which tracking or disturbance rejection is required, and also by the frequency of any unstable poles \citep{Houpis_1991_DigitalControlSystems}. It therefore follows that a combination of low frequency zeros (which impose a large $NT_s$), and higher frequency performance specifications or unstable poles (which impose a low $T_s$), would lead unavoidably to a large preview length ($N$).% in order to achieve 95\% of the maximum available benefit due to preview.

### 2008-09-25 Latex/H2Preview/H2PrevSummary.tex
Version sent to David 25/9/08

\psfrag{xp}{$\ma{r(k-N)\\\vdots\\r(k-1)}$}

@@

\includegraphics[width=0.5\columnwidth]{./diags/PrevContStructxpKbar.eps}

@@

\end{figure}}
\item[The optimal control is independent of $W_r$ for large $N$]

@@

\item[Preview only improves low frequency tracking performance.] For a low-pass plant, high frequency tracking performance is limited by the prohibitive size of the control action. This is a fundamental feature of the plant and cannot be changed by anticipative action. This effect is illustrated in Figure~\ref{fig:sigmah2}, where preview improves the low-frequency performance by reducing the magnitude of both the tracking error and the control signal. %The price for this improvement appears to be larger control action at higher frequencies

@@

Previously, the addition of integral action has been approached in an {LQG} setting through the use of the differentiated control signal in the cost function \citep[e.g. ][]{Tomizuka_1979_IntegralPreviewFI,Katayama_1987_PreviewAndIntegral,Tomi_1980_FFPrev}. Such an approach does not allow one to adjust the strength of the integral action, which could lead to difficulty in satisfying stability/performance requirements.

>>>>

\psfrag{xpr}{$\ma{r(k-N)\\\vdots\\r(k)}$}

@@

\includegraphics[width=0.42\columnwidth]{./diags/PrevContStructxpKbar.eps}

@@

\end{figure}}\item[The optimal control is independent of $W_r$ for large $N$]

@@

\item[Preview only improves low frequency tracking performance.] For a low-pass plant, high frequency tracking performance is limited by the prohibitive amplitude of the control action. This is a fundamental feature of the plant and cannot be changed by anticipative action. This effect is illustrated in Figure~\ref{fig:sigmah2}, where preview improves the low-frequency performance by reducing the magnitude of both the tracking error and the control signal. %The price for this improvement appears to be larger control action at higher frequencies

@@

Previously, the addition of integral action has been approached in an {LQG} setting through the use of the differentiated control signal in the cost function \citep[e.g. ][]{Tomizuka_1979_IntegralPreviewFI,Katayama_1987_PreviewAndIntegral,Tomi_1980_FFPrev}. Such an approach does not allow one to adjust the strength of the integral action, which is likely to lead to difficulty in satisfying stability/performance requirements.
